STAT 133 Final Project: Visualizing Berkeley Police Data

### 2016-08-09 final_paper/finalpaper.Rmd
Rebecca: editing

```{r, warning = FALSE, echo = F, fig.width = 10, fig.height = 5, message = FALSE, fig.align="center", fig.cap= "Berkeley Police Stops"}
map_stop1
```

@@

```{r, warning = FALSE, echo = F, fig.width = 10, fig.height = 5, message = FALSE, fig.align="center", fig.cap= "2015-2016 Police Stop Density (left) and 2010 Census Tract Population Density (right)"}
grid.arrange(stopdensitymap4, popdenmap, ncol=2)
```

@@

```{r, fig.height = 3, fig.width = 12, echo=FALSE, warning = FALSE, message = FALSE, fig.align="center", fig.cap= "Police Stop density map VS. Population Density"}
stopdensitymap3 
```

>>>>

```{r, warning = FALSE, echo = F, fig.width = 10, fig.height = 5, message = FALSE, fig.align="center", fig.cap= "Berkeley Police Stops"}
map_stop1 # figure 5
```

@@

```{r, warning = FALSE, echo = F, fig.width = 10, fig.height = 5, message = FALSE, fig.align="center", fig.cap= "2015-2016 Police Stop Density (left) and 2010 Census Tract Population Density (right)"}
grid.arrange(stopdensitymap4, popdenmap, ncol=2) # figure 6
```

@@

```{r, fig.height = 3, fig.width = 12, echo=FALSE, warning = FALSE, message = FALSE, fig.align="center", fig.cap= "Police Stop Density Map by race"}
stopdensitymap3 # figure 7
```
